---
title: 'Project: Shiny Application and Reproducible Pitch '
author: "Rajan Makadia"
date: "Aug 31, 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
always_allow_html: yes
---

```{r setup, include=FALSE}
summary(mtcars)
```

## Assignment: 

- This is the final presentaion of the Course Project.

- The  course is focused on  "Developing Data Products".

- The main objective of the Project is to Crate a Shiny application  and Creat a presentation in Slidify or Rstudio Presenter to pitch for the application.

## Application Functionality

The site is providing a tool to plot values of two variables.
It requires your inputs prefrence like miles per galon, cylinders, hp, etc. 
It's needed to plot the graph based on the both varialbe measures selected.
                                  

## mtcars dataset

The data used in this app comes from  "mtcars" dataset in RStudio. 

```{r cars, echo = TRUE}
summary(mtcars)
```

## The Application URL and Source Code:

- The application can be found on Shynyapps.io website.
https://rx2131.shinyapps.io/Assignment4/

- The source code is available on GitHub Repository:
https://github.com/rx2131/Data_Science

- The presentation can be found on Rpubs
http://rpubs.com/rx2131/Assignment4_Presentation